\section{Energy Minimization}

\cite{smina}

There are two buttons available at the bottom of the right sidebar. The "Save" button allows the results to be saved in their current state; this generates a single file in sdf format that contains all the structures that were returned by the query. The structures are sorted in the output in the same order that they are sorted in the sidebar. Pressing the "Minimize" button before saving allows the user to assess the favorability of the interaction between the protein and the ligands returned by the search. This feature energy minimizes the results using smina, a fork of AutoDock Vina, using the default Vina scoring function. Using this scoring function, a more negative score indicates that the corresponding interaction is more favorable according to the scoring function's model of protein-ligand interaction; thus large positive scores indicate unfavorable interactions, and large negative scores indicate more favorable interactions. If the user chooses to minimize the results, they may be sorted by score or RMSD of the minimized pose from the starting pose (which was aligned to the query) by pressing the name of the sorting method. Additional filters may also be applied by setting values for maximum score, maximum minimized RMSD, and requesting that only one pose be retained for each conformer. Once the filters have been set as desired, the user should press "Apply" to enforce them. Pressing "Save" after minimizing the results generates a single sdf file containing the minimized structures that includes their minimized scores; it is often useful to rank the structures in order of increasing score so that the best results can be reviewed first. We additionally recommend that results be filtered by mRMSD (e.g. 2Å) to eliminate poses with significant deviations from the original query. 