\section{Energy Minimization}

The query-aligned poses returned by pharmacophore and shape search are fully determined by the query. They are not influenced by interactions with the receptor.  Furthermore, although the pose of the result is optimized to match the query, the conformation of the result is taken directly from the pre-generated conformers of the search database.  Energy minimization of results optimizes both the pose and conformation of identified hits with respect to the provided receptor using the AutoDock Vina \cite{Trott_2009} scoring function and smina \cite{smina}, a fork of AutoDock Vina with enhanced minimization functionality. 

Minimized compounds adopt a conformation at a local minimum identified by performing gradient descent on the energy surface starting from the initial query aligned pose.
Results are sorted according to predicted binding affinity in kcal/mol (more negative values are more favorable).  Also reported is a minimized RMSD (mRMSD) that is the RMSD between the query-aligned pose and the minimized pose.  This provides an indication of how far the compound has deviated from the original query.  Minimized results may be sorted and filtered by affinity and mRMSD to eliminate poses with unfavorable binding energies (e.g., $>-6$ kcal/mol) and significant deviations from the original query (e.g. 2{\AA}). An example of an energy minimized compound is shown in Figure~\ref{minfig} and contrasted with the unminimized pharmacophore aligned pose. The complete set of minimized compound structures can be saved, including scoring annotations, as a compressed SDF structure file.